\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-21 main.tex
Minor edits..

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose content from attacker controlled input containing syntax of a foreign 
format, thereby creating a polyglot. The polyglot is benign when viewed as the 
original format, but malicious when viewed as the injected format. While the 
targeted service serves the content as its original format, it is in the hands 
of the attacker to decide how it is interpreted. Examples of 
such services include dynamic user driven websites, e.g. social networks, search engines, etc.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. Hence, for the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
the injected format will pose as a new context, unknown to the filter. Chances are that the 
key elements of the injected format will pass the filter unaltered.

@@

When a PDF document is embedded in a web page, the corresponding plugin 
is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
that the plug-in is selected based 
on the MIME-type, either supplied by the server or in the type attribute
%
with preference for the later.
%
Also recall
that the browser rely on the plug-in to handle the situation when the MIME-type 
supplied by the server is inconsistent with the MIME-type of the plug-in.
In the case of the Adobe Reader plug-in, it disregards the MIME-type
supplied by the server and will attempt to interpret any content as PDF. 
Listing~\ref{lst:embed-pdf} shows how 
arbitrary content can be rendered as PDF format.

>>>>

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose content from attacker controlled input containing syntax of a foreign 
format, thereby creating a polyglot. The polyglot is benign when viewed as the 
original format, but malicious when viewed as the injected format. While the 
targeted service serves the content as its original format, it is in the hands 
of the attacker to decide how it is interpreted. Examples of 
such services include social networks, search engines, i.e., nearly any dynamic user driven website.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. Hence, for the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
the injected format will pose as a new context, unknown to the filter. Chances are that the 
key elements of the injected format will pass the filter unaltered.

@@

When a PDF document is embedded in a web page, the corresponding plug-in 
is executed to render the content. Recall from Section~\ref{sec:cross-origin} 
that the plug-in is selected based 
on the MIME-type, either supplied by the server or in the type attribute
%
with preference for the later.
%
Also recall
that the browser rely on the plug-in to handle the situation when the MIME-type 
supplied by the server is inconsistent with the MIME-type of the plug-in.
In the case of the Adobe Reader plug-in, it disregards the MIME-type
supplied by the server and will attempt to interpret any content as PDF. 
Listing~\ref{lst:embed-pdf} shows how 
arbitrary content can be rendered as PDF format.
